Structured Versus Decorated Cospans

### 2020-11-19 cospans.tex
erased previous proof (for different direction functor), refer here if we need anything

Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}. Indeed, $\lE_0=\mathrm{id}_\A$ is a symmetric monoidal functor trivially. For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans
\begin{align*}
\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\mathbf{1}\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m') \\
\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',\phi_{m,m'}(x,x'))}_{\cref{eq:explicitstructure2}}\leftarrow(b+b',\bot_{b+b'})\Big)%=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')
\end{align*}
which are essentially the same. {\chris Well they look equal to me...thoughts?} Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration
$$\mathbf{1}\xrightarrow{\phi_0}F(0_A)\xrightarrow{F(\mathrm{id})}F(0_A)$$
which is essentially the same as $\lE((0_A,\phi_0)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$ again by \cref{eq:explicitstructure2}.

 First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$. The diagrams utilizing these maps that are required to commute do so trivially.

For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \maps U_{1_{F\lCsp}} \to \mathbb{E}(U_{1_{_L \lCsp(\X)}})$ where the horizontal 1-cell $U_{1_{F\lCsp}}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\A$};
\node (B) at (1,0) {$1_\A$};
\node (C) at (2,0) {$1_\A$};
\node (D) at (3,0) {$!_{1_{\A}} \in F(1_\A)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\]
where $!_{1_{\A}} = \phi \maps 1 \to F(1_\A)$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$. The horizontal 1-cell $U_{1_{_L \lCsp(\X)}}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(1_\A)$};
\node (B) at (1,0) {$L(1_\A)$};
\node (C) at (2,0) {$L(1_\A)$};
%\node (D) at (3,0.5) {$I \in F(1_\mathrm{A})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\]
where here we make use of the fact that the left adjoint $L \maps (\A,+,1_\A) \to (\X,+,1_\X)$ preserves all colimits and thus $L(1_\A) \cong 1_\X$. The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\X)}})$ is then given by the pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\A$};
\node (B) at (1.25,0) {$R(L(1_\A))$};
\node (C) at (2.5,0) {$1_\A$};
\node (D) at (4.5,0) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{${\eta_{1_\A}}$} (B)
(C) edge node[above]{${\eta_{1_\A}}$} (B);
\end{tikzpicture}
\]
The isomorphism $\delta$ is then given by the 2-morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\A$};
\node (B) at (1,0) {$1_{\A}$};
\node (C) at (2,0) {$1_\A$};
\node (A') at (0,-1) {$1_\A$};
\node (B') at (1,-1) {$R(L(1_\A))$};
\node (C') at (2,-1) {$1_\A$};
\node (D) at (3,0) {$!_{1_\A} \in F(1_\A)$};
\node (D') at (3.75,-1) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A') edge node[above]{${\eta_{1_\A}}$} (B')
(C') edge node[above]{${\eta_{1_\A}}$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{${\eta_{1_\A}}$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
$$\tau_{{\eta_{1_\A}}} \maps F({\eta_{1_\A}})(!_{1_\A})) \to !_{R(L(1_\A))}$$
of $F\lCsp$. This is just the natural isomorphism $\mathbb{E}_{1_\A}$ from earlier.

Given two horizontal 1-cells $M$ and $N$ of $_L \lCsp(\X)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(c_2)$};
\node (D) at (3,0) {$L(c_1')$};
\node (E) at (4,0) {$x'$};
\node (F) at (5,0) {$L(c_2')$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(D) edge node[above]{$i'$} (E)
(F) edge node[above]{$o'$} (E);
\end{tikzpicture}
\]
their images $\mathbb{E}(M)$ and $\mathbb{E}(N)$ are given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$R(x)$};
\node (C) at (2,0) {$c_2$};
\node (D) at (3,0) {$c_1'$};
\node (E) at (4,0) {$R(x')$};
\node (F) at (5,0) {$c_2'$};
\node (G) at (1,-0.5) {$x \in F(R(x))$};
\node (H) at (4,-0.5) {$x' \in F(R(x'))$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
(D) edge node[above]{$R(i') \eta_{c_1'}$} (E)
(F) edge node[above]{$R(o') \eta_{c_2'}$} (E);
\end{tikzpicture}
\]
and so $\mathbb{E}(M) \otimes \mathbb{E}(N)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1+c_1'$};
\node (B) at (3.25,0) {$R(x)+R(x')$};
\node (C) at (6.5,0) {$c_2+c_2'$};
\node (D) at (3.25,-0.5) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$}; 
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(i) \eta_{c_1} +R(i') \eta_{c_1'}$} (B)
(C) edge node[above]{$R(o) \eta_{c_2} + R(o) \eta_{c_2'}$} (B);
\end{tikzpicture}
\]
where $$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x'} F(R(x)) \times F(R(x')) \xrightarrow{\phi_{R(x),R(x')}} F(R(x)+R(x')).$$ On the other hand, $M \otimes N$ is given by
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1+c_1')$};
\node (B) at (2,0) {$x+x'$};
\node (C) at (4,0) {$L(c_2+c_2')$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$(i+i')\phi_{c_1,c_1'}^{-1}$} (B)
(C) edge node[above]{$(o+o')\phi_{c_2,c_2'}^{-1}$} (B);
\end{tikzpicture}
\]
and $\mathbb{E}(M \otimes N)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1+c_1'$};
\node (B) at (4,0) {$R(x+x')$};
\node (C) at (8,0) {$c_2+c_2'$};
\node (D) at (4,-0.5) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+x')).$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B)
(C) edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B);
\end{tikzpicture}
\]
We then have a 2-isomorphism $\mu_{M,N} \maps E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $F\lCsp$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (-2.5,0) {$c_1+c_1'$};
\node (B) at (1,0) {$R(x)+R(x')$};
\node (C) at (4.5,0) {$c_2+c_2'$};
\node (A') at (-2.5,-1) {$c_1+c_1'$};
\node (B') at (1,-1) {$R(x+x')$};
\node (C') at (4.5,-1) {$c_2+c_2'$};
\node (D) at (6.55,0) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$};
\node (D') at (6.55,-1) {$d_{\mathbb{E}(M \otimes N)} \in F(R(x+x'))$};
\node (E) at (2,-1.5) {$\tau_\mu \maps F(\kappa)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(i)\eta_{c_1} + R(i')\eta_{c_1'}$} (B)
(C) edge node[above]{$R(o)\eta_{c_2} + R(o')\eta_{c_2'}$} (B)
(A') edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B')
(C') edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$\kappa$} (B')
(C) edge node [right]{$1$} (C');
\end{tikzpicture}
\]
where $\kappa$ is the isomorphism which comes from $R \maps \X \to \A$ preserving finite colimits.

The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square. 
%Kenny: I think this might be a good place to cut the monoidal stuff.
%Christina: Deal! They are right below.
To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \lCsp(\X)$ given by:
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$x_1$};
\node (C) at (2,0) {$L(c_1')$};
\node (D) at (3,0) {$L(c_2)$};
\node (E) at (4,0) {$x_2$};
\node (F) at (5,0) {$L(c_2')$};
\node (G) at (6,0) {$L(c_3)$};
\node (H) at (7,0) {$x_3$};
\node (I) at (8,0) {$L(c_3')$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
(D) edge node[above]{$i_2$} (E)
(F) edge node[above]{$o_2$} (E)
(G) edge node[above]{$i_3$} (H)
(I) edge node[above]{$o_3$} (H);
The left unitality square:
\node (A) at (0,0) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
\node (B) at (3,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
\node (C) at (0,-1) {$\mathbb{E}(M_1)$};
\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
(A) edge node[above]{$\delta \otimes 1$} (B)
(B) edge node[right]{$\mu_{1,M_1}$} (D)
(A) edge node[left]{$\lambda'$} (C)
(D) edge node[above]{$\mathbb{E}(\lambda)$} (C);
has an underlying diagram of maps of cospans given by:
			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
			\node (a) at (-6,0) {$1_\A+c_1$};
			\node (b) at (-0.5,0) {$R(L(1_\A)) + R(x_1)$};
			\node (c) at (5,0) {$1_\A+c_1'$};
			\node (d2) at (7.5,1) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
			\node (a2) at (-6,1) {$1_\A+c_1$};
			\node (b2) at (-0.5,1) {$1_\A+R(x_1)$};
			\node (c2) at (5,1) {$1_\A+c_1'$};
			\node (d3) at (7.5,2) {$\mathbb{E}(M_1)$};
                                \node (a3) at (-6,2) {$c_1$};
			\node (b3) at (-0.5,2) {$R(x_1)$};
			\node (c3) at (5,2) {$c_1'$};
			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
                                \node (a5) at (-6,-1) {$1_\A+c_1'$};
			\node (b5) at (-0.5,-1) {$R(L(1_\A)+x_1)$};
			\node (c5) at (5,-1) {$1_\A+c_1'$};
			\node (d5) at (7.5,-2) {$\mathbb{E}(M_1)$};
                                \node (a6) at (-6,-2) {$c_1$};
			\node (b6) at (-0.5,-2) {$R(x_1)$};
			\node (c6) at (5,-2) {$c_1'$};
			(d2) edge node [left]{$\lambda$} (d3)
			(d2) edge node [left] {$\delta \otimes 1$} (d)
			(d) edge node [left] {$\mu_{1,M_1}$} (d4)
			(d4) edge node [left] {$\mathbb{E}(\lambda)$} (d5)
			(a) edge node[above]{$\eta_{1_\A}+R(i_1)\eta_{c_1}$} (b)
			(c) edge node[above]{$\eta_{1_\A}+R(o_1)\eta_{c_1'}$} (b)
                                (a2) edge node[above]{$1+R(i_1)\eta_{c_1}$} (b2)
			(c2) edge node[above]{$1+R(o_1)\eta_{c_1'}$} (b2)
                                (a2) edge node[left]{$1$} (a)
                                (b2) edge node[left]{$\eta_{1_\A}+1$} (b)
(b2) edge node[right]{$\tau_2$} (b)
			(c2) edge node[right]{$1$} (c)
                                (a3) edge node[above]{$R(i_1)\eta_{c_1}$} (b3)
			(c3) edge node[above]{$R(o_1)\eta_{c_1'}$} (b3)
                                (a2) edge node[left]{$\lambda_{\A}$} (a3)
                                (b2) edge node[left]{$\lambda_{\A}$} (b3)
(b2) edge node[right]{$\tau_1$} (b3)
			(c2) edge node[right]{$\lambda_{\A}$} (c3)
                                (a5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(i_1)\eta_{c_1})$} (b5)
			(c5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(o_1)\eta_{c_1'})$} (b5)
                                (a) edge node[left]{$1$} (a5)
                                (b) edge node[left]{$\mu_{L(1_\A),x_1}$} (b5)
			(c) edge node[right]{$1$} (c5)
                                (a6) edge node[above]{$R(i_1)\eta_{c_1}$} (b6)
			(c6) edge node[above]{$R(o_1)\eta_{c_1'}$} (b6)
                                (a5) edge node[left]{$\lambda_{\A}$} (a6)
                                (b5) edge node[left]{$R(\lambda_{\X})$} (b6)
 (b5) edge node[right]{$\tau_4$} (b6)
			(c5) edge node[right]{$\lambda_{\A}$} (c6);
with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_1))$:
\node (A) at (-.5,0) {$F(\lambda_{\A})(!_{1_\A}+x_1)$};
\node (C) at (4,0) {$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(!_{R(L(1_\A))} +x_1$)};
\node (D) at (-.5,-1) {$x_1$};
\node (E) at (4,-1) {$F(R(\lambda_\X))(x_{!+1})$};
(A) edge node[above]{$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(\tau_2)$} (C)
(A) edge node[left]{$\tau_1$} (D)
(E) edge node[above]{$\tau_4$} (D)
(C) edge node[right]{$F(R(\lambda_\X))(\tau_3)$} (E);
where $x_{!+1}$ is the decoration $x_1$ on the object $R(L(1_\A)+x_1) \in \A$. The above square commutes because $$F(\lambda_\A)(!_{1_\A}+x_1) = F(R(\lambda_\X)(\mu_{L(1_\A),x_1})(\eta_{1_\A}+1))(!_{1_\A}+x_1)$$ as the corresponding left unitality square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes. The right unitality square is similar. The associator hexagon:
\node (A) at (0,0) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
\node (B) at (3.5,0) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
\node (C) at (7,0) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
\node (A') at (0,-1) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
\node (B') at (3.5,-1) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
\node (C') at (7,-1) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
(A) edge node[above]{$\mu_{M_1,M_2} \otimes 1$} (B)
(B) edge node[above]{$\mu_{M_1 \otimes M_2,M_3}$} (C)
(A') edge node[above]{$1 \otimes \mu_{M_2,M_3}$} (B')
(B') edge node[above]{$\mu_{M_1,M_2 \otimes M_3}$} (C')
(A) edge node [left]{$a'$} (A')
(C) edge node [right]{$\mathbb{E}(a)$} (C');
has underlying maps of cospans given by:
\node(d) at (1.5,7) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
\node (d2) at (1.5,8) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
\node (d3) at (1.5,9) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
\node (d4) at (1.5,10) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
\node (d5) at (1.5,6) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
\node (d6) at (1.5,5) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
\node (d7) at (1.5,4) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
			\node (a) at (-4.25,0) {$(c_1+c_2)+c_3$};
			\node (b) at (2.5,0) {$(R(x_1)+R(x_2))+R(x_3)$};
			\node (c) at (9.25,0) {$(c_1'+c_2')+c_3'$};
			\node (a2) at (-4.25,1) {$(c_1+c_2)+c_3$};
			\node (b2) at (2.5,1) {$R(x_1+x_2)+R(x_3)$};
			\node (c2) at (9.25,1) {$(c_1'+c_2')+c_3'$};
                                \node (a3) at (-4.25,2) {$(c_1+c_2)+c_3$};
			\node (b3) at (2.5,2) {$R((x_1+x_2)+x_3)$};
			\node (c3) at (9.25,2) {$(c_1'+c_2')+c_3'$};
                                \node (a4) at (-4.25,3) {$c_1+(c_2+c_3)$};
			\node (b4) at (2.5,3) {$R(x_1+(x_2+x_3))$};
			\node (c4) at (9.25,3) {$c_1' + (c_2' + c_3')$};
                                \node (a5) at (-4.25,-1) {$c_1+(c_2+c_3)$};
			\node (b5) at (2.5,-1) {$R(x_1)+(R(x_2)+R(x_3))$};
			\node (c5) at (9.25,-1) {$c_1' + (c_2' + c_3')$};
                                \node (a6) at (-4.25,-2) {$c_1+(c_2+c_3)$};
			\node (b6) at (2.5,-2) {$R(x_1)+R(x_2+x_3)$};
			\node (c6) at (9.25,-2) {$c_1' + (c_2' + c_3')$};
                                \node (a7) at (-4.25,-3) {$c_1+(c_2+c_3)$};
			\node (b7) at (2.5,-3) {$R(x_1+(x_2+x_3))$};
			\node (c7) at (9.25,-3) {$c_1' + (c_2' + c_3')$};
(d) edge node[left] {$\mu_{M_1,M_2} \otimes 1$} (d2)
(d2) edge node[left] {$\mu_{M_1 \otimes M_2,M_3}$} (d3)
(d3) edge node[left] {$\mathbb{E}(a)$} (d4)
(d) edge node[left] {$a'$} (d5)
(d5) edge node[left] {$1 \otimes \mu_{M_2,M_3}$} (d6)
(d6) edge node[left] {$\mu_{M_1,M_2 \otimes M_3}$} (d7)
			(a) edge node[above]{$(R(i_1)\eta_{c_1}+R(i_2)\eta_{c_2})+R(i_3)\eta_{c_3}$} (b)
			(c) edge node[above]{$(R(o_1)\eta_{c_1'}+R(o_2)\eta_{c_2'})+R(o_3)\eta_{c_3'}$} (b)
                                (a2) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}+R(i_3)\eta_{c_3}$} (b2)
			(c2) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}+R(o_3)\eta_{c_3'}$} (b2)
                                (a) edge node[left]{$1$} (a2)
                                (b) edge node[left]{$\kappa + 1$} (b2)
			(c) edge node[right]{$1$} (c2)
                                (a3) edge node[above]{$R((i_1+i_2)+i_3)\eta_{(c_1+c_2)+c_3}$} (b3)
			(c3) edge node[above]{$R((o_1+o_2)+o_3)\eta_{(c_1'+c_2')+c_3'}$} (b3)
                                (a2) edge node[left]{$1$} (a3)
                                (b2) edge node[left]{$\kappa$} (b3)
			(c2) edge node[right]{$1$} (c3)
                                (a4) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b4)
			(c4) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b4)
                                (a3) edge node[left]{$a_\A$} (a4)
                                (b3) edge node[left]{$R(a_\X)$} (b4)
			(c3) edge node[right]{$a_\A$} (c4)
                                (a5) edge node[above]{$R(i_1)\eta_{c_1}+(R(i_2)\eta_{c_2}+R(i_3)\eta_{c_3})$} (b5)
			(c5) edge node[above]{$R(o_1)\eta_{c_1'}+(R(o_2)\eta_{c_2'}+R(o_3)\eta_{c_3'})$} (b5)
                                (a) edge node[left]{$a_\A$} (a5)
                                (b) edge node[left]{$a_\A$} (b5)
			(c) edge node[right]{$a_\A$} (c5)
                                (a6) edge node[above]{$R(i_1)\eta_{c_1}+R(i_2+i_3)\eta_{c_2+c_3}$} (b6)
			(c6) edge node[above]{$R(o_1)\eta_{c_1'}+R(o_2+o_3)\eta_{c_2'+c_3'}$} (b6)
                                (a5) edge node[left]{$1$} (a6)
                                (b5) edge node[left]{$1+\kappa$} (b6)
			(c5) edge node[right]{$1$} (c6)
                                (a7) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b7)
			(c7) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b7)
                                (a6) edge node[left]{$1$} (a7)
                                (b6) edge node[left]{$\kappa$} (b7)
			(c6) edge node[right]{$1$} (c7);
Here we have omitted the natural isomorphisms $\phi_{c_i,c_j} \maps L(c_i) + L(c_j) \to L(c_i + c_j)$ on the inward pointing morphisms which make up the legs of each cospan due to limited space. The corresponding maps of decorations amount to the following commutative diagram in $F(R(x_1+(x_2+x_3)))$:
\node (A) at (0,0) {$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3)$};
\node (B) at (5,0) {$F((R(a_\mathrm{X}))(\kappa))((x_1+x_2)+x_3)$};
\node (C) at (5,-1) {$F(R(a_\mathrm{X}))((x_1+x_2)+x_3)$};
\node (D) at (5,-2) {$x_1+(x_2+x_3)$};
\node (E) at (0,-1) {$F((\kappa)(1+\kappa))((x_1+x_2)+x_3)$};
\node (F) at (0,-2) {$F(\kappa)(x_1+(x_2+x_3))$};
(A) edge node[above]{$F((R(a_\X))(\kappa))(\tau_1)$} (B)
(B) edge node[right]{$F(R(a_\X))(\tau_2)$} (C)
(C) edge node[right]{$\tau_3$} (D)
(A) edge node[left]{$F((\kappa)(1+\kappa))(\tau_4)$} (E)
(E) edge node[left]{$F(\kappa)(\tau_5)$} (F)
(F) edge node[above]{$\tau_6$} (D);
The above square commutes because $$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3) = F((R(a_\X))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes. Lastly, the braiding square:
\node (A) at (0,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
\node (B) at (3,0) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
\node (C) at (0,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
\node (D) at (3,-1) {$\mathbb{E}(M_2 \otimes M_1)$};
(A) edge node[above]{$\beta'$} (B)
(B) edge node[right]{$\mu_{M_2,M_1}$} (D)
(A) edge node[left]{$\mu_{M_1,M_2}$} (C)
(C) edge node[above]{$\mathbb{E}(\beta)$} (D);
has underlying map of cospans given by:
\node (d) at (7,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
\node (d2) at (7,1) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
\node (d3) at (7,2) {$\mathbb{E}(M_2 \otimes M_1)$};
\node (d4) at (7,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
\node (d5) at (7,-2) {$\mathbb{E}(M_2 \otimes M_1)$};
			\node (a) at (-4,0) {$c_1+c_2$};
			\node (b) at (0.5,0) {$R(x_1)+R(x_2)$};
			\node (c) at (5,0) {$c_1'+c_2'$};
			\node (a2) at (-4,1) {$c_2+c_1$};
			\node (b2) at (0.5,1) {$R(x_2)+R(x_1)$};
			\node (c2) at (5,1) {$c_2'+c_1'$};
                                \node (a3) at (-4,2) {$c_2+c_1$};
			\node (b3) at (0.5,2) {$R(x_2+x_1)$};
			\node (c3) at (5,2) {$c_2' + c_1'$};
                                \node (a5) at (-4,-1) {$c_1+c_2$};
			\node (b5) at (0.5,-1) {$R(x_1+x_2)$};
			\node (c5) at (5,-1) {$c_1'+c_2'$};
                                \node (a6) at (-4,-2) {$c_2+c_1$};
			\node (b6) at (0.5,-2) {$R(x_2+x_1)$};
			\node (c6) at (5,-2) {$c_2' + c_1'$};
(d) edge node[left]{$\beta'$} (d2)
(d2) edge node[left]{$\mu_{M_2,M_1}$}(d3)
(d) edge node[left] {$\mu_{M_1,M_2}$}(d4)
(d4)edge node[left]{$\mathbb{E}(\beta)$}(d5)
			(a) edge node[above]{$R(i_1) \eta_{c_1} + R(i_2)\eta_{c_2}$} (b)
			(c) edge node[above]{$R(o_1) \eta_{c_1'} + R(o_2) \eta_{c_2'}$} (b)
                                (a2) edge node[above]{$R(i_2) \eta_{c_2} + R(i_1) \eta_{c_1}$} (b2)
			(c2) edge node[above]{$R(o_2) \eta_{c_2'} + R(o_1) \eta_{c_1'}$} (b2)
                                (a) edge node[left]{$\beta_\A$} (a2)
                                (b) edge node[left]{$\beta_\A$} (b2)
			(c) edge node[right]{$\beta_\A$} (c2)
                                (a3) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b3)
			(c3) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b3)
                                (a2) edge node[left]{$1$} (a3)
                                (b2) edge node[left]{$\kappa$} (b3)
			(c2) edge node[right]{$1$} (c3)
                                (a5) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}$} (b5)
			(c5) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}$} (b5)
                                (a) edge node[left]{$1$} (a5)
                                (b) edge node[left]{$\kappa$} (b5)
			(c) edge node[right]{$1$} (c5)
                                (a6) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b6)
			(c6) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b6)
                                (a5) edge node[left]{$\beta_\A$} (a6)
                                (b5) edge node[left]{$R(\beta_\X)$} (b6)

>>>>

Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}. Indeed, $\lE_0=\mathrm{id}_\A$ is a symmetric monoidal functor trivially. For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans
\begin{align*}
\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\mathbf{1}\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m') \\
\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',\phi_{m,m'}(x,x'))}_{\cref{eq:explicitstructure2}}\leftarrow(b+b',\bot_{b+b'})\Big)%=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')
\end{align*}
which are essentially the same. {\chris Well they look equal to me...thoughts?} Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration
$$\mathbf{1}\xrightarrow{\phi_0}F(0_A)\xrightarrow{F(\mathrm{id})}F(0_A)$$
which is essentially the same as $\lE((0_A,\phi_0)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$ again by \cref{eq:explicitstructure2}.
\end{proof}
